Cluster Difference Imaging Photometric Survey. I. Light Curves of Stars in Open Clusters from TESS Sectors 6 \& 7

### 2019-08-18 paper_I/ms.tex
aas journals: submitted!
to ApJS, but we'll see what the editors think

The Transiting Exoplanet Survey Satellite (TESS,
\citealt{ricker_transiting_2015}) holds the promise to deliver the
most homogeneous and comprehensive cluster photometric survey in
history.  Based on the cluster membership data of
\citet{Kharchenko_et_al_2013}, approximately $2\times10^5$ open
cluster members brighter than $T=16$ will be observed in the
full-frame images (FFIs) over the first two years of TESS
observations.  This count includes the ``most probable'' members,
which by the \citet{kharchenko_global_2012} definition requires the
independent kinematic, photometric, and spatial membership
probabilities to each exceed 61\%.  The actual number of stars in
clusters is larger, as the membership catalogs are not yet complete,
even at these relatively bright magnitudes \citep[{\it
e.g.},][]{roser_nine_RSG_2016,cantat-gaudin_gaia_2018,cantat-gaudin_newOCs_2019,kounkel_untangling_2019,sim_open_2019}.

A major barrier to deriving precise photometry from the TESS images is
the relatively poor angular resolution ($21''$ per pixel).   The
problems with crowding and complex backgrounds are so severe that the
TESS Candidate Target List deprioritizes 2-minute targets within
$15^\circ$ of the galactic plane\footnote{During the first year of
TESS observations, objects within $15^\circ$ of the galactic plane
were deprioritized. Starting in the second year of observations, the
cutoff changed to objects within $10^\circ$ of the galactic plane
\citep{stassun_TIC8_2019}.}~\citep{stassun_TIC_2018,stassun_TIC8_2019}.
This decision was made because the large pixel size and the high
stellar surface density make aperture photometry unreliable.  However,
it implies that most stars in clusters, which are usually near
the galactic plane, will go unprocessed by the official {\it TESS}
data reduction pipeline.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\gridline{\fig{target_star_cumulative_counts.pdf}{0.43\textwidth}{}}
		\vspace{-0.8cm}
		\gridline{\fig{target_star_hist_logt.pdf}{0.43\textwidth}{}}
		\vspace{-0.8cm}
		\gridline{\fig{target_star_reference_pie_chart.pdf}{0.43\textwidth}{}}
	\end{center}
	\vspace{-0.8cm}
	\caption{
		Target star statistics.
		{\it Top.} Cumulative counts as a function of apparent Gaia $Rp$-band
		magnitude.  
		{\it Middle.} Histogram of target star ages, for the subset of
		stars with ages matched against \citet{Kharchenko_et_al_2013}.
		{\it Bottom.} Provenance of cluster membership.  Percentages are
		relative to $N_{\rm total}=1{,}061{,}446$ target stars. Symbols
		are as follows.
		D14 is \citet{dias_proper_2014}.
		K13 is \citet{Kharchenko_et_al_2013}.
		CG18 is \citet{cantat-gaudin_gaia_2018}.
		Z18 is \citet{zari_3d_2018}, with upper main sequence and
		pre-main-sequence samples sub-divided.
		``$\geq 2$'' indicates at least two authors reported a star as a
		candidate cluster member.
		%``Other'' refers to sources enumerated in \S~\ref{sec:starselection}.
		\label{fig:cdips_targets}
	}
\end{figure}

@@

\begin{figure}[!t]
	\gridline{\fig{astromresidual_hist.pdf}{0.45\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{astromresidual_quiver.pdf}{0.5\textwidth}{}}
  %\vspace{-0.8cm}
	%\gridline{\fig{astromresidual_apertures.pdf}{0.5\textwidth}{}}
	\vspace{-0.8cm}
    \caption{
		{\it Top.} Histogram of astrometric residual. The $x$-axis shows 
		the distance between the measured centroid positions of stars, 
		compared to the predicted positions from the WCS solution.
    {\it Bottom.} Vector plot of astrometric residual. Each arrow is
    the vector from the measured to the projected star position.
    Directions are correct, but lengths are 50 times their true size
    for visualization purposes.  The systematic error in the top-right
    corner is a typical problem generic to wide-field astrometry.  The
    frame chosen for this plot is the photometric reference frame used
    for Sector 6, Camera 1, CCD 1; we automatically impose cutoffs on
    the median and $90^{\rm th}$ percentile of the astrometric
    residual in order to ensure similar levels of astrometric
    precision are maintained throughout the reduction.
	}
	\label{fig:astromresid}
\end{figure}

@@

We then reduced TESS full frame images taken over the course of about
two months (Sectors 6 and 7; the first fields close to the galactic
plane).  We performed difference imaging in order to deal with the
complex background.  Using forced aperture photometry, we made light
curves for all Gaia-DR2 sources brighter than $G_{\rm Rp}$ of 13, and went three
magnitudes deeper for our target star sample.  This yielded \numberlcs
target star light curves across \numberclusters distinct
clusters.

@@

Most of these pipelines are geared towards tasks more general than our
own, and most use aperture photometry.  The SPOC pipeline produces the
calibrated FFIs from raw images, processes 2 minute data, identifies
exoplanets, and produces the TESS data products of record.  The
MIT-QLP processes a subset of stars on the FFIs, identifies
exoplanets, and the affiliated TESS Science Office alerts object of
interest for ground and space-based followup.  The \texttt{eleanor}
pipeline is a user-friendly tool for extracting light curves from the
FFIs.  The team developing \texttt{eleanor} is also reporting planet candidates
to ExoFOP-TESS\footnote{\url{exofop.ipac.caltech.edu/tess/index.php}}.  The TASOC pipeline is primarily aimed at
asteroseismology and also includes classification modules for many types of variable stars. The
\citeauthor{oelkers_precision_2018} pipeline was aimed at broad,
all-sky variability searches, and used difference imaging methods
similar to our own.  Finally, the Padova team's effort is also
directed towards star clusters, but uses PSF subtraction to mitigate
crowding.  As light curves from these groups continue to be released, this ecosystem should provide many opportunities to compare and improve data analysis techniques.

@@

In future work, these concerns will likely drive us to expand beyond the current
sample of target stars.  For the time being, the
light curves are of sufficient quality to begin astrophysical studies.  We
invite any who wish to explore the time evolution of stellar or
exoplanetary systems to interact with the data at \stscilink.

@@

	\tablecomments{
		Table~\ref{tbl:s6_lcs} is published in its entirety in a machine-readable format.
		A portion is shown here for guidance regarding its form and content.
		Names are matched against \citet{Kharchenko_et_al_2013} as
		described in Appendix~\ref{appendix:uniquenames}, and $N_{\rm lc}$
		is the number of light curves associated with the cluster from this
		data release.
		The description column matches \citet{Kharchenko_et_al_2013},
		and is in the format ``\texttt{a},\texttt{b},\texttt{c},\texttt{d}''.
		Meanings of displayed symbols are as follows.
		\texttt{a}:
		``='' = cluster parameters were determined,
		``\&'' = duplicated/coincides with other cluster;
		\texttt{b}:
		``blank'' = open cluster,
		``a'' =	association,
		``m'' =	moving group,
		``n'' =	nebulosity;
		\texttt{c}:
		``o'' = object,
		``c'' = candidate;
		\texttt{d}:
		``ass'' =	stellar association,
		``var'' =	clusters with variable extinction.
	}

>>>>

The Transiting Exoplanet Survey Satellite (TESS,
\citealt{ricker_transiting_2015}) holds the promise to deliver the
most homogeneous and comprehensive cluster photometric survey in
history.  Based on the cluster membership data of
\citet{Kharchenko_et_al_2013}, approximately $2\times10^5$ open
cluster members brighter than $T=16$ will be observed in the
full-frame images (FFIs) over the first two years of TESS.  This count includes the
\citeauthor{Kharchenko_et_al_2013} ``most probable'' members, which
are stars
with kinematic, photometric, and spatial membership
probabilities each independently exceeding 61\% \citep{kharchenko_global_2012}.  The
actual number of stars in clusters is likely larger, as the membership
catalogs are not yet complete, even within the nearest kiloparsec
\citep[{\it
e.g.},][]{roser_nine_RSG_2016,cantat-gaudin_gaia_2018,cantat-gaudin_newOCs_2019,kounkel_untangling_2019,sim_open_2019}.

A major barrier to deriving precise photometry from the TESS images is
the relatively poor angular resolution ($21''$ per pixel).   The
problems with crowding and complex backgrounds are so severe that the
TESS Candidate Target List deprioritizes 2-minute targets within
$15^\circ$ of the galactic plane\footnote{During the first year of
TESS observations, objects within $15^\circ$ of the galactic plane
were deprioritized. Starting in the second year of observations, the
cutoff changed to objects within $10^\circ$ of the galactic plane
\citep{stassun_TIC8_2019}.}~\citep{stassun_TIC_2018,stassun_TIC8_2019}.
This decision was made because the large pixel size and the high
stellar surface density make aperture photometry unreliable. 
By consequence, most stars in clusters, which are usually near
the galactic plane, will go unprocessed by the official {\it TESS}
data reduction pipeline.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\gridline{\fig{target_star_cumulative_counts.pdf}{0.42\textwidth}{}}
		\vspace{-0.8cm}
		\gridline{\fig{target_star_hist_logt.pdf}{0.42\textwidth}{}}
		\vspace{-0.8cm}
		\gridline{\fig{target_star_reference_pie_chart.pdf}{0.42\textwidth}{}}
	\end{center}
	\vspace{-0.8cm}
	\caption{
		Target star statistics.
		{\it Top.} Cumulative counts as a function of apparent Gaia $Rp$-band
		magnitude.  
		{\it Middle.} Histogram of target star ages, for the subset of
		stars with ages matched against \citet{Kharchenko_et_al_2013}.
		{\it Bottom.} Provenance of cluster membership.  Percentages are
		relative to the $N_{\rm total}=1{,}061{,}446$ target stars, which are listed in
		Table~\ref{tbl:cdips_targets}. Symbols
		are as follows.
		D14 is \citet{dias_proper_2014}.
		K13 is \citet{Kharchenko_et_al_2013}.
		CG18 is \citet{cantat-gaudin_gaia_2018}.
		Z18 is \citet{zari_3d_2018}, with upper main sequence and
		pre-main-sequence samples sub-divided.
		``$\geq 2$'' indicates at least two authors reported a star as a
		candidate cluster member.
		%``Other'' refers to sources enumerated in \S~\ref{sec:starselection}.
		\label{fig:cdips_targets}
	}
\end{figure}

@@

\begin{figure}[!t]
	\gridline{\fig{astromresidual_hist.pdf}{0.45\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{astromresidual_quiver.pdf}{0.5\textwidth}{}}
  %\vspace{-0.8cm}
	%\gridline{\fig{astromresidual_apertures.pdf}{0.5\textwidth}{}}
	\vspace{-0.8cm}
    \caption{
		{\it Top.} Histogram of astrometric residual. The $x$-axis shows 
		the distance between the measured centroid positions of stars, 
		compared to the predicted positions from the WCS solution.
    {\it Bottom.} Vector plot of astrometric residual. Each arrow is
    the vector from the measured to the projected star position.
    Directions are correct, but lengths are 50 times their true size
    for visual clarity.  The systematic error in the top-right
    corner is a typical problem generic to wide-field astrometry.  The
    frame chosen for this plot is the photometric reference frame used
    for Sector 6, Camera 1, CCD 1; we automatically impose cutoffs on
    the median and $90^{\rm th}$ percentile of the astrometric
    residual in order to ensure similar levels of astrometric
    precision are maintained throughout the reduction.
	}
	\label{fig:astromresid}
\end{figure}

@@

We then reduced TESS full frame images taken over the course of about
two months (Sectors 6 and 7; the first fields close to the galactic
plane).  We performed difference imaging to deal with the complex
background.  Using forced aperture photometry, we made light curves
for all Gaia-DR2 sources brighter than $G_{\rm Rp}$ of 13, and went
three magnitudes deeper for our target star sample.  This yielded
\numberlcs target star light curves across \numberclusters distinct
clusters.  The number of light curves per cluster was reported
(Tables~\ref{tbl:s6_lcs} and~\ref{tbl:s7_lcs}).  The software
developed for the reduction is available online
\citep{bhatti_cdips-pipeline_2019}.

@@

Most of these pipelines are geared towards tasks more general than our
own, and most use aperture photometry.  The SPOC pipeline produces the
calibrated FFIs from raw images, processes 2 minute data, identifies
exoplanets, and produces the TESS data products of record.  The
MIT-QLP processes a subset of stars on the FFIs, identifies
exoplanets, and the affiliated TESS Science Office alerts object of
interest for ground and space-based followup.  The \texttt{eleanor}
pipeline is a user-friendly tool for extracting light curves from the
FFIs.  The team developing \texttt{eleanor} is also reporting planet
candidates to
ExoFOP-TESS\footnote{\url{exofop.ipac.caltech.edu/tess/index.php}}.
The TASOC pipeline is primarily aimed at asteroseismology and includes
classification modules for many types of variable stars. The
\citeauthor{oelkers_precision_2018} pipeline was aimed at broad,
all-sky variability searches, and used difference imaging methods
similar to our own.  Finally, the Padova team's effort is also
directed towards star clusters, but uses PSF subtraction to mitigate
crowding.  As light curves from these groups continue to be released,
this ecosystem should provide many opportunities to compare and
improve data analysis techniques.

@@

In future work, these concerns will likely drive us to expand beyond
the current sample of target stars.  For the time being, the light
curves are of sufficient quality and quantity to begin astrophysical
studies.  We invite any who wish to explore the time evolution of
stellar or exoplanetary systems to interact with the data at
\stscilink.

@@

	\tablecomments{
		Table~\ref{tbl:s6_lcs} is published in its entirety in a machine-readable format.
		The top twenty entries are shown here for guidance regarding form and content.
		Names are matched against \citet{Kharchenko_et_al_2013} as
		described in Appendix~\ref{appendix:uniquenames}, and $N_{\rm lc}$
		is the number of light curves associated with the cluster from this
		data release.
		The description column matches \citet{Kharchenko_et_al_2013},
		and is in the format ``\texttt{a},\texttt{b},\texttt{c},\texttt{d}''.
		Meanings of displayed symbols are as follows.
		\texttt{a}:
		``='' = cluster parameters were determined,
		``\&'' = duplicated/coincides with other cluster;
		\texttt{b}:
		``blank'' = open cluster,
		``a'' =	association,
		``m'' =	moving group,
		``n'' =	nebulosity;
		\texttt{c}:
		``o'' = object,
		``c'' = candidate;
		\texttt{d}:
		``ass'' =	stellar association,
		``var'' =	clusters with variable extinction.
	}
